---
title: "Programs for Nowcasting"
author: "Joaquin Salas"
date: "12 de julio de 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#In R
## update files
EstimateDelaysUpdate.Rmd, updates the observation of confirmed positives by date of onset. Located: E:\\Documents\\informs\\research\\2020.06.05 delays\\code 
It generates <2ndStage_updated_delays.csv>

#In Matlab
#Model
*delay.compoundRateOfChange2* takes <2ndStage_updated_delays.csv> and compute the parameters for the Gamma distributions in the file <GammaParam.csv> and the variable <theta>

## Current infectious number
*delay.nowcastingCompound* uses the Gamma distributions to update the current estimate for each day producing in the process uncertainty areas around the mean.

## Infectious sequences
*delay.nowcastingSamples* takes the parameters for the Gamma distributions and generates 1,000 sequences of random number of infectious. The sequences are saved in <infectious_samples.csv>

#In R
Go back to R and execute the follwing program

## Nowcasting
Execute the program *estimateRtMexicoNowcasting.Rmd*, in the E:\\Documents\\informs\\research\\2020.05.18 prediction\\code directory. This program will run the *EpiEstim* program to compute $R_t$.


```{r cars}
 
 
```
 
